Turbulence in compact to giant HII regions

### 2022-04-15 strucfunc_paper.tex
Reorganize results figures - move corner plots to appendix

\newcommand\sffig[1]{%
  \begin{tabular}{@{}ll@{}}
    (a)& (b)\\
    \includegraphics[width=0.45\linewidth]{Figures/sf-emcee-#1}
       &  \includegraphics[width=0.45\linewidth]{Figures/corner-emcee-#1}
  \end{tabular}%
}

\begin{figure*}
  \centering
  \sffig{OrionS}
  \caption{
    Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line from Orion core region.
  }
  \label{fig:strucfunc-fit-OrionS}
\end{figure*}
\begin{figure*}
  \centering
  \sffig{M8}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Lagoon Nebula. 
  }
  \label{fig:strucfunc-fit-M8}
\end{figure*}
\begin{figure*}
  \centering
  \sffig{CarC}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Carina Nebula. 
  }
  \label{fig:strucfunc-fit-CarC}
\end{figure*}

\begin{figure*}
  \centering
  \sffig{N346}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the NGC~346 nebula in the SMC. 
  }
  \label{fig:strucfunc-fit-N346}
\end{figure*}
\begin{figure*}
  \centering
  \sffig{Dor}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the 30~Doradus nebula in the LMC Nebula. 
  }
  \label{fig:strucfunc-fit-Dor}
\end{figure*}

\begin{figure*}
  \centering
  \sffig{HV}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Hubble~V nebula.
  }
  \label{fig:strucfunc-fit-HV}
\end{figure*}
\begin{figure*}
  \centering
  \sffig{HX}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the Hubble~X nebula.
  }
  \label{fig:strucfunc-fit-HX}
\end{figure*}

\begin{figure*}
  \centering
  \sffig{N595}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the NGC~595 nebula.
  }
  \label{fig:strucfunc-fit-N595}
\end{figure*}
\begin{figure*}
  \centering
  \sffig{N604H}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the NGC~604 nebula.
  }
  \label{fig:strucfunc-fit-N604H}
\end{figure*}

\begin{figure*}
  \centering
  \sffig{OrionLH}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-OrionS} except for the extended Orion Nebula.
  }
  \label{fig:strucfunc-fit-OrionLH}
\end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-A}
%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-A}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-B}
%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-B}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-C}
%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-C}
% \end{figure*}

% \begin{figure*}
%   \centering
%   \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-D}
%   \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-D}
% \end{figure*}

@@

>>>>

\newlength\SFwidth
\setlength\SFwidth{0.45\textwidth}
\newcommand\SFtwograph[2]{%
  \includegraphics[width=\SFwidth]{Figures/sf-emcee-#1}
  &  \includegraphics[width=\SFwidth]{Figures/sf-emcee-#2}
}
\newcommand\SFtwocorner[2]{%
  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#1}
  &  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#2}
}

\newcommand\sffigg[2]{%
  \begin{tabular}{@{}ll@{}}
    (a)& (b)\\
    \SFtwograph{#1}{#2}
  \end{tabular}%
}
\newcommand\sffigggg[4]{%
  \begin{tabular}{@{}ll@{}}
    (a)& (b)\\
    \SFtwograph{#1}{#2}\\
    (c)& (d)\\
    \SFtwograph{#3}{#4}\\
  \end{tabular}%
}
\newcommand\sfcfig[1]{%
  \includegraphics[width=\SFwidth]{Figures/corner-emcee-#1}%
}  
\newcommand\sfcfigg[2]{%
  \begin{tabular}{@{}ll@{}}
    (a)& (b)\\
    \SFtwocorner{#1}{#2}
  \end{tabular}%
}
\newcommand\sfcfigggg[4]{%
  \begin{tabular}{@{}ll@{}}
    (a)& (b)\\
    \SFtwocorner{#1}{#2}\\
    (c)& (d)\\
    \SFtwocorner{#3}{#4}\\
  \end{tabular}%
}

\begin{figure*}
  \centering
  \sffigggg{OrionS}{M8}{OrionLH}{CarC}
  \caption{
    Second-order structure functions
    for the velocity centroid images
    of the \ha{} emission line
    from Galactic \hii{} regions.
  }
  \label{fig:strucfunc-fit-Galactic}
\end{figure*}
\begin{figure}
  \centering
  \includegraphics[width=\SFwidth]{Figures/corner-emcee-OrionS}
  \caption{
    Example corner plot of covariances between
    model parameters of fits to the \ha{} structure function.
    The example shown is for Orion,
    while figures for the remaining regions are given in
    Appendix~\ref{sec:addit-covar-corn}. 
  }
  \label{fig:corner-example-Orion}
\end{figure}

\begin{figure*}
  \centering
  \sffigg{N346}{Dor}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-Galactic}
    except for Magellanic Cloud \hii{} regions. 
  }
  \label{fig:strucfunc-fit-MC}
\end{figure*}

\begin{figure*}
  \centering
  \sffigggg{HV}{HX}{N595}{N604H}
  \caption{
    Same as figure~\ref{fig:strucfunc-fit-Galactic}
    except for \hii{} regions in more distant
    Local Group Galaxies.
  }
  \label{fig:strucfunc-fit-ExtraGal}
\end{figure*}

@@

\section{Additional covariance corner plots for model fits}
\label{sec:addit-covar-corn}
Supplementary online-only material.
\clearpage

\begin{figure*}
  \centering
  \sfcfigggg{OrionS}{M8}{OrionLH}{CarC}
  \caption{
    Corner plots of covariances between
    fitted model parameters
    of \ha{} structure function
    for Galactic \hii{} regions.
  }
  \label{fig:corner-Galactic}
\end{figure*}

\begin{figure*}
  \centering
  \sfcfigg{N346}{Dor}
  \caption{
    Same as figure~\ref{fig:corner-Galactic}
    except for Magellanic Cloud \hii{} regions. 
  }
  \label{fig:corner-MC}
\end{figure*}

\begin{figure*}
  \centering
  \sfcfigggg{HV}{HX}{N595}{N604H}
  \caption{
    Same as figure~\ref{fig:corner-Galactic}
    except for \hii{} regions in more distant
    Local Group Galaxies.
  }
  \label{fig:corner-ExtraGal}
\end{figure*}
